---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# qacdata

<!-- badges: start -->
<!-- badges: end -->

## Overview

`qacdata` is an R data package for datasets used by students of [Passion Driven Statistics](https://passiondrivenstatistics.com/). This package allows for the concise searching and downloading of relevant data from the following sources:

* [Federal Reserve Economic Data (FRED)](https://fred.stlouisfed.org/): economic time-series data
* [World Development Indicators (WDI)](https://datacatalog.worldbank.org/dataset/world-development-indicators): collection of development indicators, compiled from officially-recognized international sources
* [addhealth](https://www.cpc.unc.edu/projects/addhealth/documentation/publicdata): developmental and health trajectories across the life course of adolescence into young adulthood (Wave 4)
* marscrater: global database for Mars that contains 378,540 craters statistically complete for diameters D ≥ 1 km
* [cttraffic](https://data.ct.gov/Public-Safety/Racial-Profiling-Prohibition-Project-Traffic-Stop-/g7s9-f7az): racial profiling prohibition project traffic stop data


## Installation

You can install the development version from [GitHub](https://github.com/fredcorpuz06/qacdata) with:

``` r
# install.packages("devtools")
devtools::install_github("fredcorpuz06/qacdata")
```
## Usage

```{r example}
library(qacdata)

data_search("education", c("FRED", "WDI"))

data_download("AddHealth", "H4TR10", "H4CJ5")
```

## Getting help

If you encounter a clear bug, please file a minimal reproducible example on [github](https://github.com/fredcorpuz06/qacdata/issues). 
