---
title: "Introduction to qacdata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Data Search: Finding interesting variables
```{r setup, warning = FALSE, message = FALSE}
library(qacdata)
library(dplyr)
```


Let's begin by examining the `AddHealth` dataset
```{r}
qacdata::addhealth
```

There are `r dim(qacdata::addhealth)[2]` columns/variables in this dataset. Normally, we would find variables of interesting by finding the codebook online or accessing a PDF version and hitting *Ctrl + F*. With the `qacdata` packing this search can be done in R

```{r}
data_search("birth", "AddHealth")

```
We find 45 possible variables within the `AddHealth` dataset that's description contains the word "birth". `H4TR10` by its description is on "How many live births resulted from (this pregnancy/these pregnancies)?". 

If there are more variables that can we viewed on your console, evoke the `View` function. 
```{r eval=FALSE}
View(data_search("sex", "AddHealth"))
```
"H4SE27" seems interesting. Let's find more about it

```{r}
data_search("sex", "AddHealth") %>% 
  get_description("H4SE27")
```
Lets grab both columns and work with them.


## Data Download: get data and visualize

First let's download the data
```{r}
data_download("AddHealth", "H4TR10") 
```


Let's recode missing values based on the information we got from the `get_note` function
```{r}
data_search("birth", "AddHealth") %>% 
  get_note("H4TR10")
  
data_search("sex", "AddHealth") %>% 
  get_note("H4SE27")

cleaned_df <- data_download("AddHealth", "H4TR10", "H4SE27") %>% 
  transmute(births = ifelse(H4TR10 >= 96, NA, H4TR10),
         sex = ifelse(H4SE27 >= 8, NA, H4SE27)) 
cleaned_df
```


Now we are ready to visualize
```{r}
library(ggplot2)
theme_set(theme_light())
cleaned_df %>% 
  na.omit() %>% 
  count(births, sex) %>% 
  ggplot(aes(x = births, y = n, fill = factor(sex))) +
  geom_col() +
  labs(title = "Nonsense graph for illustration purposes",
       x = "Category of live birthds",
       y = "Count",
       fill = "Sex Freq")
```

