---
title: "Untitled"
author: "Frederick"
date: "11/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(ggplot2)
theme_set(theme_light())

source("wdi_api.r")
source("utils.r")
```

# Download quant data
```{r}
# "http://api.worldbank.org/countries/all/indicators/4.1_TOTAL.EDU.SPENDING?format=json&per_page=2500&date=1950:2019"
indicators <- data_search("poverty")
View(indicators)

INDICATOR <- "1.0.PSev.1.90usd"

wdi_rez <- data_download(INDICATOR) %>% 
  filter_mostly_missing(country, value, perc = 0.2)

wdi_rez 
wdi_rez %>% 
  ggplot(aes(date, value)) + 
  geom_line() + 
  facet_wrap(~ country) +
  labs(title = get_title(indicators, INDICATOR))


##----------
## World Map
##----------
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)
world <- ne_countries(scale = 110, returnclass = "sf")
map_data <- wdi_rez %>% 
  left_join(countries %>% select(name, longitude, latitude), by = c("country" = "name")) %>% 
  mutate_at(vars(contains("ude")), as.double)

bounds <- map_data %>%
  group_by(country)  %>% 
  summarise(longitude = first(longitude),
            latitude = first(latitude)) %>% 
  ungroup() %>% 
  summarise(max_long = max(longitude, na.rm = TRUE),
            max_lat = max(latitude, na.rm = TRUE),
            min_long = min(longitude, na.rm = TRUE),
            min_lat = min(latitude, na.rm = TRUE))

ggplot(world) +
  geom_sf() + 
  geom_point(data = map_data, aes(x = longitude, y = latitude), size = 2, color = "red") + 
  coord_sf(xlim = c(bounds$min_long, bounds$max_long),
           ylim = c(bounds$min_lat, bounds$max_lat)) + 
  labs(title = paste(get_title(indicators, INDICATOR), sep = ": "), 
       x = "", 
       y = "")



```











Frequency: For fetching quarterly (Q), monthly (M) or yearly (Y) values. This feature currently works along with MRV. This query string is useful for querying high frequency data.

Example: http://api.worldbank.org/v2/en/country/ind;chn/indicator/DPANUSSPF?mrv=7&frequency=M

Multiple Indicators: Data for multiple indicators can be queried from a single data source by providing the indicator codes separated by ";" (semicolon), as well as the source ID.

Example: http://api.worldbank.org/v2/country/chn;ago/indicator/AG.AGR.TRAC.NO;SP.POP.TOTL?source=2
Note: A maximum of 60 indicators can be used. A maximum of 1,500 characters are allowed between two back-slashes (/). A maximum of 4,000 characters are allowed in the entire URL.